### 2024-08-26 paper.tex
comment out section

\section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
TODO: I am unsure why this section is interesting or what to say about it.
Should I delete it?
For now I will ignore it and try to make the paper flow nicely without it.

Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
% First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).

\begin{lemma}\label{sl2_triple}
    There is exactly one way to choose \(H, F \in \gl_{m + n}\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
\end{lemma}
\begin{proof}
Suppose we have \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
Writing \(F =: \begin{pmatrix}
    F_{11} & F_{12} \\
    F_{21} & f
\end{pmatrix}\), and similarly for \(H\), we have
\[2E = [H, E] = \begin{pmatrix}
    0 & H_{12}e \\
    0 & he
\end{pmatrix} - \begin{pmatrix}
    0 & 0 \\
    e H_{21} & eh
\end{pmatrix},\]
\[H = [E, F] = \begin{pmatrix}
    0 & 0 \\
    e F_{21} & ef
\end{pmatrix} - \begin{pmatrix}
    0 & F_{12}e \\
    0 & fe
\end{pmatrix}.\]
From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in \cref{simple_sl2_triple}.
We also see that \(H_{11} = 0\).
Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
% Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
Then our final constraint is that 
\[-2F = [H, F] = \]
\[\begin{pmatrix}
    H_{12} F_{21} & H_{12} F_{22} \\
    H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
\end{pmatrix} - \begin{pmatrix}
    F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
    F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
\end{pmatrix}.\]
Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
Substituting in the equation above then,
\[-2F = \begin{pmatrix}
    F_{12} e F_{21} & F_{12}e f \\
    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
\end{pmatrix} - \begin{pmatrix}
    F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
    f eF_{21} & F_{21} F_{12}e + fh
\end{pmatrix} =\]
\[\begin{pmatrix}
    0 & F_{12}(fe + h) \\
    eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
\end{pmatrix} - \begin{pmatrix}
    0 & F_{11} F_{12}e + F_{12} h \\
    (ef - h)F_{21} & F_{21} F_{12}e + fh
\end{pmatrix} =\]
\[\begin{pmatrix}
    0 & F_{12}fe \\
    eF_{21} F_{11} & eF_{21} F_{12} + hf
\end{pmatrix} - \begin{pmatrix}
    0 & F_{11} F_{12}e \\
    ef F_{21} & F_{21} F_{12}e + fh
\end{pmatrix}.\]
Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
This shows that \(H_{12} = H_{21} = 0\).
We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
\end{proof}

>>>>

% \section{Finding \(\spl_2\)-triples \((E, H, F)\) in \(\gl_{m + n}\) with a particular \(E\).}
% TODO: I am unsure why this section is interesting or what to say about it.
% Should I delete it?
% For now I will ignore it and try to make the paper flow nicely without it.

% Let \(E = \begin{pmatrix}0 & 0 \\ 0 & e\end{pmatrix} \in \gl_{m + n}\).
% We will show that there is exactly one \(\spl_2\)-triple \((E, H, F)\), and we will find what it looks like.
% % First we solve the case \(m = 0\) (so \(E = e\)), and then we use this to solve the case of arbitrary \(m\).

% \begin{lemma}\label{sl2_triple}
%     There is exactly one way to choose \(H, F \in \gl_{m + n}\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
% \end{lemma}
% \begin{proof}
% Suppose we have \(H, F\) so that \((E, H, F)\) is an \(\spl_2\)-triple.
% Writing \(F =: \begin{pmatrix}
%     F_{11} & F_{12} \\
%     F_{21} & f
% \end{pmatrix}\), and similarly for \(H\), we have
% \[2E = [H, E] = \begin{pmatrix}
%     0 & H_{12}e \\
%     0 & he
% \end{pmatrix} - \begin{pmatrix}
%     0 & 0 \\
%     e H_{21} & eh
% \end{pmatrix},\]
% \[H = [E, F] = \begin{pmatrix}
%     0 & 0 \\
%     e F_{21} & ef
% \end{pmatrix} - \begin{pmatrix}
%     0 & F_{12}e \\
%     0 & fe
% \end{pmatrix}.\]
% From these we observe that \((e, h, f)\) must also be an \(\spl_2\)-triple, so \(h, f\) must be as in \cref{simple_sl2_triple}.
% We also see that \(H_{11} = 0\).
% Recalling that left multiplication by \(e\) is a down-shift, and right multiplication is a left-shift, we see that \(H_{12}\) is all zeroes except for the leftmost column, and \(H_{21}\) is all zeroes except for the bottom row.
% % Then \(F_{12}\) must be all zeros except for the two leftmost columns, and \(F_{21}\) must be all zeroes except for the bottom two rows.
% Then our final constraint is that 
% \[-2F = [H, F] = \]
% \[\begin{pmatrix}
%     H_{12} F_{21} & H_{12} F_{22} \\
%     H_{21} F_{11} + H_{22} F_{21} & H_{21} F_{12} + H_{22} F_{22}
% \end{pmatrix} - \begin{pmatrix}
%     F_{12} H_{21} & F_{11} H_{12} + F_{12} H_{22} \\
%     F_{22} H_{21} & F_{21} H_{12} + F_{22} H_{22}
% \end{pmatrix}.\]
% Now \(H_{12} = F_{12}e\), and \(H_{21} = eF_{21}\), from the equation \(H = [E, F]\).
% Substituting in the equation above then,
% \[-2F = \begin{pmatrix}
%     F_{12} e F_{21} & F_{12}e f \\
%     eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
% \end{pmatrix} - \begin{pmatrix}
%     F_{12} e F_{21} & F_{11} F_{12}e + F_{12} h \\
%     f eF_{21} & F_{21} F_{12}e + fh
% \end{pmatrix} =\]
% \[\begin{pmatrix}
%     0 & F_{12}(fe + h) \\
%     eF_{21} F_{11} + h F_{21} & eF_{21} F_{12} + hf
% \end{pmatrix} - \begin{pmatrix}
%     0 & F_{11} F_{12}e + F_{12} h \\
%     (ef - h)F_{21} & F_{21} F_{12}e + fh
% \end{pmatrix} =\]
% \[\begin{pmatrix}
%     0 & F_{12}fe \\
%     eF_{21} F_{11} & eF_{21} F_{12} + hf
% \end{pmatrix} - \begin{pmatrix}
%     0 & F_{11} F_{12}e \\
%     ef F_{21} & F_{21} F_{12}e + fh
% \end{pmatrix}.\]
% Now we see that \(F_{11} = 0\), and consequently that \(F_{12} = F_{21} = 0\) as well.
% This shows that \(H_{12} = H_{21} = 0\).
% We conclude that \(H\) and \(F\) just have \(h\) and \(f\) in their bottom-right corners, respectively.
% \end{proof}
